---
title: 'Group Assignment 3'
author: 'Group 2'
date: "2021/2/5"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

  In this group work, we will study the relationship between the new crown epidemic in the United States in the past year and the predictors we selected. First, we will select five predictor variables and explain why we chose these five variables. After that, we will build our theory, how the predictor variables we choose will be related to the dependent variable (COVID-19 case data). The data sets we use are county.data and covid.smooth.data_county.
  
  After establishing the theory. We will review the selected variables. We will analyze the mean, median and other data of variables and build their distribution diagrams. After that, we will use the glm() function and build a regression model to fit these predictors. Finally we will write down the main findings.
  
# Predictors select and Theory
  The five factors we used in this assignment is:
  Economic typology 2015 
  POP ESTIMATE 2018 
  POVALL_2018 
  Unemployment_rate_2018 
  Density per square mile of land area - Population 
  
  Economic typology 2015 tells us a economic type of a specific county, it's based on farming, mining, manufacturing or recreation. We believe that the economic structure plays a crucial role in the spread of COVID-19. Because the economic structure dominated by recreation will temporarily close entertainment venues due to the outbreak of the new crown epidemic. For counties that are dominated by agriculture, because the United States has a very high level of agricultural automation, the labor force is relatively not very dense. As a result, counties dominated by agriculture and counties dominated by entertainment industry may have less spread of COVID-19. As a negative case, labor-intensive industries dominated by manufacturing may be the hardest hit by COVID-19. Because factories are usually indoors and have limited floor space, it is difficult for people to maintain a certain social distance. This might caused the spread of COVID-19.
  
  By comparing the total population with the total number of COVID-19 confirmed cases, we can find out which states/counties have spread COVID-19 and summarize our findings based on other data.
  
  The total poor population is a very meaningful data. During the COVID-19 pandemic, people with high incomes can choose not to work or work from home. But for the poor, their work is mainly labor work, so they cannot work at home. This may also be a factor in the spread of COVID-19.
  
  The unemployment rate is a relatively meaningful data. Unemployment means that people do not have stable jobs, and some people choose to go out for odd jobs, which will affect the spread of COVID-19. Others have no money to pay their bills because they are unemployed. According to our speculation, this group of people does not pay much attention to the protection of their own health (such as wearing masks). This may also be a factor leading to the spread of COVID-19.
  
  Population density is a very meaningful data for the study of the spread of COVID-19. According to the US Centers for Disease Control and Prevention, most of the spread of the COVID-19 in the United States is family transmission. This means that areas with high population density may have a higher rate of transmission of the COVID, and areas with low population density may have a lower rate of transmission of COVID.
  
  To sum up, as our theory, in terms of economic structure, the more labor-intensive economic structure, we speculate that the higher the transmission rate of COVID-19. For the poor, we believe that areas with more poor people have a higher transmission rate of COVID-19. The spread of COVID-19 will also be high in areas with high unemployment. The spread of COVID-19 will be higher in areas with higher population density. Finally, we will compare them based on the total population.
  


## Process the table covid.smooth.data_county
```{r}
library(tidyverse)

load('Data/covid.RData')
load("Data/county.data.RData")

covid.smooth.data_county$new.cases[is.na(covid.smooth.data_county$new.cases)] <- 0

covid.smooth.data_county.1 <- covid.smooth.data_county %>%
  group_by(county_state,county, state) %>%
  summarise(tot_cases = sum(new.cases))
 
```



## Process the data in county.data
```{r}

#remove suffix
patterns <- c(" County| Parish| Borough| City and Borough| Municipality| Census Area| Parish")

county.data.1 <- county.data%>%
  mutate(county_name = gsub(patterns, "", Area_Name))%>%
  dplyr::select(FIPS,  Area_Name, county_name, State, Economic_typology_2015, POP_ESTIMATE_2018, POVALL_2018, Unemployment_rate_2018, Density.per.square.mile.of.land.area...Population)

#remove the city suffix except some specific cities
for(i in 1:nrow(county.data.1)){
  if(county.data.1[i,]$county_name != "Baltimore city" & county.data.1[i,]$county_name != "St. Louis city" & county.data.1[i,]$county_name != "Fairfax city" & county.data.1[i,]$county_name != "Franklin city" & county.data.1[i,]$county_name != "Richmond city" & county.data.1[i,]$county_name != "Roanoke city"){
    county.data.1[i,]$county_name = gsub(" city", "", county.data.1[i,]$county_name)
  }
}

county.data.1$county_name = gsub(" city", " City", county.data.1$county_name)

#add state suffix
state_name <- ""
for(i in 1:nrow(county.data.1)){
  if(county.data.1[i,]$FIPS != 0 & county.data.1[i,]$FIPS%%1000 == 0){
    state_name <- county.data.1[i,]$Area_Name
  }
  else{
    county.data.1$county_state[i] = paste0(county.data.1[i,]$county_name, ", ", state_name)
  }
}

county.data.2 <- county.data.1%>%
  dplyr::select(FIPS, county_state, Economic_typology_2015, POP_ESTIMATE_2018, POVALL_2018, Unemployment_rate_2018, Density.per.square.mile.of.land.area...Population)

```

## merge county with covid
```{r}
covid.with.count.data <- merge(county.data.2,
covid.smooth.data_county.1 , by="county_state", duplicateGeoms = TRUE)
```




# Descriptive Analysis

## Look at some of the descriptive results for your chosen variables, including their distributions as well
as their relationship to the confirmed cases variable. Plot these.
```{r Analysis}
#提取5个自变量，1个因变量，避免污染原数据
vars_chosen <- covid.with.count.data  %>% 
  dplyr::rename(economic_type = Economic_typology_2015, 
                population    = POP_ESTIMATE_2018 ,
                poverty       = POVALL_2018 ,
                unemployment  = Unemployment_rate_2018 ,
                pop_density   = Density.per.square.mile.of.land.area...Population,
                tot_cases     = tot_cases) %>%
  dplyr::select(economic_type, population, poverty, unemployment,
                pop_density, tot_cases)
  

```


```{r descriptive analysis}
variable <-c('economic_type','population','poverty','unemployment','pop_density')
summary(vars_chosen[variable], na.rm=TRUE)

library(psych)
psych::describe(vars_chosen[variable])
```

## Analysis
  According to the data and graph given above, the mean of economic in 2015 is 1.81 and a standard deviation of 1.82 and the data is little dispersed, min is 0 and max is 5. The distribution shows a right skew (skewness +0.45) and is slightly flatter than the normal distribution (kurtosis -1.30)
The mean of population is 104123.67 and a standard deviation of 33581.38 the weekly rent is largely dispersed; the min is 88 and max is 10105518. The distribution shows a right skew (skewness +13.56) and is steeper than the normal distribution (kurtosis 306.71).The mean of poverty is 13316.06 and a standard deviation of 45611.42 the personal income is large dispersed; min is 5 and max is 1409155. the distribution shows a serious right skew (skewness +14.71) and is steeper than the normal distribution (kurtosis 340.39).The mean of unemployment rate is 4.13 and a standard deviation of 1.50 the personal income is little dispersed; min is 1.3 and max is 19.9. the distribution shows a right skew (skewness +2.26) and is steeper than the normal distribution (kurtosis 12.46).The mean of density is 259.43 and a standard deviation of 1725.48 the personal income is large dispersed, min is 0 and max is 69468.4. the distribution shows a serious right skew (skewness +26.88) and is steeper than the normal distribution (kurtosis 930.04)


```{r convert The total cases into a categorical variable}
library(tidyverse)
tot.margins <- vars_chosen %>%
                mutate(tot.cat = dplyr::case_when(tot_cases < 864 ~ '864 and less',
                                            tot_cases >= 864 & tot_cases < 2111 ~
                                            '864 - 2,111',
                                            tot_cases >= 2111 & tot_cases < 5445 ~
                                            '2,111 - 5,445',
                                            tot_cases >= 5445 ~ '5,445 and over'),
                      tot.cat = factor(tot.cat, levels = c('864 and less',
                                                              '864 - 2,111',
                                                              '2,111 - 5,445',
                                                           '5,445 and over')))
```

Since economic type is not a continuous variable, we have to factor it out. It is found that there are more than 1,200 counties with zero industry type, accounting for the vast majority. We can see more intuitively from the second chart that the number of counties with economic type 0 is dominant. So we're going to focus on those counties. The third picture is a count chart. We can see that from the size of the red dot that a large proportion of counties with economy type 0 had more than 5,445 cases.

```{r Distributions economic_type}
eco_g <- ggplot(data = vars_chosen) + 
  geom_bar(
    mapping = aes(x = economic_type, fill = economic_type), #清洗后用病例数对应观察分布
    show.legend = FALSE,
    width = 1,
    na.rm = TRUE
  ) + 
  theme(aspect.ratio = 1) +
  labs(x = NULL, y = NULL)

eco_g + 
  labs(title = 'Economic_type Bar Plot ',
        x = 'economic_type\n') +
  coord_flip()
eco_g + 
  labs(title = 'Economic_type Polar Plot ',
        x = 'economic_type\n') +
  coord_polar()

#ggplot(data = vars_chosen, mapping = aes(x = tot_cases)) +
#  geom_freqpoly(mapping = aes(color = economic_type), binwidth = 1000000)


ggplot(data = tot.margins) +
  geom_count(mapping = aes(x = economic_type, y = tot.cat,color  = economic_type), na.rm = TRUE) +
  labs(title = 'Total Cases - Economic_type Counts Plot ',
        x = 'Economic_type\n',
        y = 'Total Cases\n')



```

In the first bar chart, counties with populations between 5,000 and 100,000 make up the majority. The study of such counties will have many positive implications. 

In the second graph. We can intuitively see that cities with a total of more than 5,445 cases are not very closely related to counties with populations between 5,000 and 100,000. Most of them have cases below 5,445. The larger counties of more than 100,000, which are the blue dots, mostly had more than 5,445 cases.

```{r Distributions population}
#Create CATegorical variable

(tot.margins <- tot.margins %>%
  mutate(pop.cate.1=dplyr::case_when(population < 5000 ~ '5,000 and less',
                   population >= 5000 & population < 100000 ~
                   'Between 5,000 & 100,000',
                   population >= 100000 & population < 500000 ~
                   'Between 100,000 & 500,000',
                   population >= 500000 ~ '500,000 and over'),
         pop.cate.1=factor(pop.cate.1, levels = c('5,000 and less',
                                        'Between 5,000 & 100,000',
                                        'Between 100,000 & 500,000',
                                        '500,000 and over'))))
(tot.margins %>%
  group_by(pop.cate.1) %>%
  tally() %>%
  ggplot(aes(x = pop.cate.1, y = n, fill = pop.cate.1)) +
  geom_bar(stat = 'identity') +
  labs(title = 'City size distribution',
        x = 'City population size\n',
        y = 'Number of cities\n') +
  theme(axis.title = element_text(face = 'bold', size=12),
        axis.text.x = element_text(size = 7)) +
  coord_flip())

ggplot(data = tot.margins) +
  geom_count(mapping = aes(x = pop.cate.1, y = tot.cat, color  = pop.cate.1))+
  labs(title = 'Total Cases - City population Counts Plot ',
        x = 'City population\n',
        y = 'Total Cases\n') +
  coord_flip()

```

In the first picture, we know that most areas have between 500 and 15,000 poor people.
In the second graph, as we can see in the rightest column, when the number of cases exceeds 5,445, the number of poor people is fairly higher.

```{r Distributions poverty}
library(Hmisc)
# 插补均值
tot.margins$poverty <- impute(tot.margins$poverty,mean)

(tot.margins <- tot.margins %>%
  mutate(pov.cate.1=dplyr::case_when(poverty < 500 ~ '5,00 and less',
                   poverty >= 500 & poverty < 15000 ~
                   '5,00 - 15,000',
                   poverty >= 15000 & poverty < 50000 ~
                   '15,000 - 50,000',
                   poverty >= 50000 & poverty < 200000 ~
                   '50,000 - 200,000',
                   poverty >= 200000 ~ '200,000 and over'),
         pov.cate.1=factor(pov.cate.1, levels = c('5,00 and less',
                                        '5,00 - 15,000',
                                        '15,000 - 50,000',
                                        '50,000 - 200,000',
                                        '200,000 and over'))))

(tot.margins%>%
  group_by(pov.cate.1) %>%
  tally() %>%
  ggplot(aes(x = pov.cate.1, y = n, fill = pov.cate.1)) +
  geom_bar(stat = 'identity') +
  labs(title = 'Poverty distribution',
        x = 'Poverty population\n',
        y = 'Number of cities\n') +
  theme(axis.title = element_text(face = 'bold', size=12),
        axis.text.x = element_text(size = 7)))

ggplot(data = tot.margins) +
  geom_count(mapping = aes(x = pov.cate.1, y = tot.cat))+
  labs(title = 'Total Cases - Poverty Counts Plot ',
        x = 'Poverty\n',
        y = 'Total Cases\n') +
  coord_flip()


```

Unemployment in most counties is less than 5%.
But in the second graph, from this we can learn that the two are highly likely to have a positive correlation. The average unemployment rate in counties with cases between 864 and 2111 was significantly higher than that in counties with cases less than 864.

```{r Distributions unemployment}
ggplot(data = tot.margins) +
  geom_bar(mapping = aes(x = unemployment, fill = unemployment), na.rm = TRUE) +
  labs(title = 'Distributions of Unemployment ',
        x = 'Unemployment Rate\n') +
  theme_minimal()

ggplot(data = tot.margins, mapping = aes(x = tot.cat, y = unemployment)) +
  geom_boxplot(na.rm = TRUE) +
  labs(title = 'Total Cases - Unemployment Rate Box Plot ',
        x = 'Total Cases\n',
        y = 'Unemployment Rate\n') +
  coord_flip()
```

As can be seen from the first bar chart, the areas with a population density of less than 121 account for the vast majority.
In the second chart, we can see a clear upward trend in the far right row of points, which indicates that the greater the population density, the more counties have more than 5,445 cases.

```{r Distributions pop_density}
# 插补均值
tot.margins$pop_density <- Hmisc::impute(tot.margins$pop_density,mean)

(tot.margins <- tot.margins %>%
    mutate(pde.cate.1=dplyr::case_when(pop_density < 44 ~ '44 and less',
                   pop_density >= 44 & pop_density < 121 ~
                   '44 - 121',
                   pop_density >= 121 & pop_density < 261 ~
                   '121 - 261',
                   pop_density >= 261 ~ '261 and over'),
         pde.cate.1=factor(pde.cate.1, levels = c('44 and less',
                                        '44 - 121',
                                        '121 - 261',
                                      '261 and over'))))
  
(tot.margins%>% 
  group_by(pde.cate.1) %>%
  tally() %>%
  ggplot(aes(x = pde.cate.1, y = n, fill = pde.cate.1)) +
  geom_bar(stat = 'identity') +
  labs(title = 'City population density distribution',
        x = 'Density\n',
        y = 'Number of cities\n') +
  theme(axis.title = element_text(face = 'bold', size=12),
        axis.text.x = element_text(size = 7)) +
  coord_flip())

ggplot(data = tot.margins) +
  geom_count(mapping = aes(x = pde.cate.1, y = tot.cat, color  = pde.cate.1))+
  labs(title = 'Total Cases - Population Density Counts Plot ',
        x = 'Density\n',
        y = 'Total Cases\n') +
  coord_flip()
```

## Patterns of 5 selected factors and total case

```{r poverty_v_opiates_mortality, warning=FALSE, echo=FALSE, message=FALSE, fig.cap = "Smoothed mortality rate as a function of proportion of families below the poverty rate and the rate of opiate prescriptions in each county. Each cell represents the mean mortality rate of a group of counties with similar values for poverty and opiate presriptions.\\label{fig:poverty_v_opiates_mortality}", fig.height= 4.5, fig.width=4, fig.align="center"}

library(ggplot2)
library(scales)
  ggplot(vars_chosen,
       aes(x = poverty / population, y = unemployment / population,
           z = tot_cases / population, alpha = tot_cases / population)) +
  stat_summary_2d(fun = mean, bins = 50) + 
  scale_fill_gradient2(low = 'grey', 
                      high = 'dark red', midpoint = 21) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) + 
  labs(title = 'Poverty and Unemployment-related COVID',
       y = 'Poverty (%)',
       x = 'Unemployment rate (%)',
       fill = 'Poverty and Unemployment-related COVID') + 
  theme_minimal() +
  theme(plot.title = element_text(size = 10, face = "bold", hjust = 0),
          strip.background = element_blank(),
          panel.border = element_blank(),
          panel.grid = element_blank(),
          axis.title = element_text(size = 8),
          legend.position = "bottom",
          axis.text = element_text(size = 7))
    
```


## Fitting Regression Model
```{r fit the first model to county, warning=FALSE, message=FALSE, cache=FALSE}
library(tidyverse)
covid.with.count.data.1 <- vars_chosen %>%
  mutate(z.economic = scale(economic_type)) %>%
  mutate(z.population = scale(population)) %>% 
  mutate(z.poverty = scale(poverty)) %>% 
  mutate(z.unemployment = scale(unemployment))%>%
  mutate(z.density = scale(pop_density))
```

```{r fitting model}
library(arm)
covid19.model <- glm(tot_cases ~ z.economic + z.population 
                     + z.poverty + z.unemployment + z.density,
                     family=poisson(link = log), 
                     data=covid.with.count.data.1)

display(covid19.model)
summary(covid19.model)
plot(covid19.model)



```

## Model Analysis
  The fitting poisson model examines the coefficient of the independent (economic ，population, poverty, unemployment rate and density)and dependent variable(total covid-19 case in different county in US). In the Poisson regression, the dependent variable is modeled in the logarithmic form of the conditional mean ln(λ). The poisson model is (tot_cases ~ z.economic + z.population + z.poverty + z.unemployment + z.density)
  
  The intercept is 8.58, the regression parameter for z. economic is -0.21, indicating that holding the other predictor variables constant, economic increase will result in a corresponding decrease in the log mean of the number of covid-19 total case probability by 0.21.The the regression parameter for z. population is 0.71, a population increase will result in a corresponding increase in the log mean of the number of covid-19 total case by 0.71.The regression parameter for z. population is -0.51, increase in poverty will result in a corresponding decrease in the log mean of the number of covid-19 total case by 0.51.
The regression parameter for z. unemployment is -0.07, increase in personal income will result in a corresponding decrease in the log mean of the number of covid-19 total case by 0.07.
  
  The regression parameter for z. density is 0.08, increase in personal income will result in a corresponding increase in the log mean of the number covid-19 total case by 0.08.


# Interactive Map

#link with shape files
```{r link us data with shape files, message=FALSE, warning=FALSE}
library(sf)

us.shape.1 <- st_read("SHP/cb_2016_us_county_20m.shp")



fip.concordance <- read.csv("Data/fips concordance.csv")



us.shape.2 <- us.shape.1 %>% 
  merge(fip.concordance %>%
          mutate(STATEFP =  ifelse(Numeric.code >= 0 & Numeric.code <= 9, 
                             paste0(0 , Numeric.code), Numeric.code)) %>%
          dplyr::rename(state = Alpha.code))






#process the table for mapping
us.shape.3 <- us.shape.2 %>%
  mutate(county_state = paste0(NAME, ", ", Name))

covid.with.county.map <- merge(us.shape.3,covid.with.count.data%>%
                                 dplyr::select(county_state, tot_cases, Economic_typology_2015, POP_ESTIMATE_2018, POVALL_2018, Unemployment_rate_2018, Density.per.square.mile.of.land.area...Population), 
                               by="county_state")


```

## Independent map
```{r map of economic type}
library(mapdeck)

key <- 'pk.eyJ1IjoiZmFuc29uZzk5NiIsImEiOiJja2tvemQ1aWcxa3o3MnBvY3JjeXdmaW1yIn0.1TaYyPHIjaCvbeL6bfJFug'
mapdeck(token = key, style = mapdeck_style("light")) %>%
  add_polygon(
    data = covid.with.county.map, 
    layer = "polygon_layer", 
    fill_colour = "Economic_typology_2015", 
    palette = "diverge_hsv", 
    fill_opacity = .9, 
    legend = TRUE,
    legend_options = list(title = "Number of confirmed cases"))

```



```{r map of dependent varaible -- tot_cases}
#map the dependent variables
library(mapdeck)


covid.with.county.map <- covid.with.county.map %>%
  mutate(tot_cases2 = cut(tot_cases, breaks=c(0, 100, 1000, 5000, 50000, 2000000),labels=c("0-100","100-1000","1000-5000","5000-50000","50000+"), include.lowest=TRUE))


key <- 'pk.eyJ1IjoiZmFuc29uZzk5NiIsImEiOiJja2tvemQ1aWcxa3o3MnBvY3JjeXdmaW1yIn0.1TaYyPHIjaCvbeL6bfJFug'
mapdeck(token = key, style = mapdeck_style("light")) %>%
  add_polygon(
    data = covid.with.county.map, 
    layer = "polygon_layer", 
    fill_colour = "tot_cases2", 
    palette = "diverge_hsv", 
    fill_opacity = .9, 
    legend = TRUE,
    legend_options = list(title = "Number of confirmed cases"))  
```

# Key Findings






